---
output:
  github_document:
    toc: TRUE
---


Performance metrics
=========


# Objective(s)
* focuses on showing the performance metrics for the following groups of models
  * [LR models: 1st, 2nd, 3rd gen, weighted average, and stacked (lasso, ridge, elasticnet)](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1008831)
  * RF models: stacked (lasso, ridge, elasticnet) stemming from this study



```{r knitr-setup, include=FALSE, eval=TRUE}
options(digits = 3)
require(knitr)
## options
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, cache = TRUE, fig.path = '../Figures/Ensembles/', fig.height = 5)
```

---------------------------------------------------------------------------------------


```{r Libraries, eval=TRUE, echo=FALSE, message=FALSE}
library(MASS)  # to use robust lm fitting in geom_smooth

library(tidyverse)

library(ggsci)

library(kableExtra)
```


# Model performance

```{r load-metrics, eval=TRUE, echo=FALSE}
# Load the performance stats for the models shown in the PloS Comput. Biol. paper (https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1008831):
prev.mods <- readr::read_csv("../Data/PreviousModelMetrics.csv", show_col_types = FALSE)

# Load the stacked RF model metrics (objects end in _metrics):
# (Assuming that you have created this RData object in the previous script; see RFEnsembles0.R)
load("StackedMetrics.RData")
```


## Individual metrics
* the larger symbols are means
  - stacked models are just one point 
* points (individual models) are jittered to avoid two much crowding due to overlap

```{r indiv-metrics-data, eval=TRUE, echo=FALSE}
# A list of the variables we want from each stats object:
vars <- c("id", "source", "cp.val", "auc", "prauc", "F1", "kap", "dp", "mcc", "Brier", "mr", "acc", "Se", "Sp", "ifd", "GM", "bac", "PM", "dpow", "DLR.pos", "DLR.neg", "DOR", "PT", "ppv", "npv", "mkd", "FM", "IMN", "NMI", "MCEN", "imcen")


vars <- c("id", "source", "cp.val", "auc", "prauc", "mcc", "Brier", "Se", "Sp", "ifd", "IMN", "MCEN")

# Combine the stats for the various models into one object:
dat <-
  dplyr::bind_rows(
    # The previously-reported models:
    prev.mods %>% dplyr::select(all_of(vars)), 
    # Stacked RF lasso:
    stack_lasso_metrics %>% dplyr::mutate(id = "RF:Lasso", source = "RF stacked (lasso)") %>%
      dplyr::select(all_of(vars)),
    # Stacked RF ridge:
    stack_ridge_metrics %>% dplyr::mutate(id = "RF:Ridge", source = "RF stacked (ridge)") %>%
      dplyr::select(all_of(vars)),
    # Stacked RF elasticnet:
    stack_en_metrics %>% dplyr::mutate(id = "RF:EN", source = "RF stacked (elasticnet)") %>%
      dplyr::select(all_of(vars))
    ) %>%
  dplyr::mutate(source = factor(source, levels = c("LR 1st generation", "LR 2nd generation", "LR 3rd generation", "LR (weighted average)", "LR stacked (lasso)", "LR stacked (ridge)", "LR stacked (elasticnet)", "RF stacked (lasso)", "RF stacked (ridge)", "RF stacked (elasticnet)")))
```



```{r indiv-metrics-function, eval=TRUE, echo=FALSE}
# NOTES:
# I have 10 different levels to display. Not ideal. There are some palettes that are capable of displaying 10 discrete levels. Some from ggsci are:
# pal_rickandmorty, pal_ucscgb, pal_igv, (pal_d3
# viridis_d can also handle 10 levels, but I did not find it all that appealing for this project.
# In the end, settled on the d3 palette from ggsci

# Note the setup in the plotMetric function below. It avoids plotting an individual point for the models (i.e. the ensembles) which have just one point.


plotMetric <- function(.x = dat, .mtc) {
  # Plots the specified metric for each model, by model generation or algorithm
  # Args:
  #  .x = tibble or data frame holding the metrics for each fit model
  #  .mtc = unquoted string for the metric
  # Returns:
  #  a dot plot of the metric values
  #
  mtc <- enquo(.mtc)
  
  # the axis label:
  .ylab <- as_label(mtc) %>% stringr::str_to_upper()
  
  # We need this object for jittering the individual points of the LR and weighted average models:
  x_sub <-
    .x %>%
    dplyr::filter(!stringr::str_detect(source, "stacked"))
  
  .x %>%
    ggplot(., aes(x = source, y = !!mtc, colour = source)) +
    # Plot the means first:
    stat_summary(fun = "mean", geom = "point", size = 5) +
    # Jitter the individual points for the LR and weighted average models:
    geom_jitter(data = x_sub, position = position_jitter(seed = 2019, width = 0.1), size = 2.5) +
    coord_flip() +
    # Setting alpha here results in both the points and means have transparency, so the means do not mask the individual points:
    scale_colour_d3(palette = c("category10"), alpha = 0.6) +  
    labs(x = NULL, y = .ylab) +
    theme_bw() +
    theme(
      legend.position = "none",
      axis.title.x = element_text(face = "bold", size = 12),
      axis.text.x  = element_text(size = 9, angle = 0),
      axis.title.y = element_text(size = 12, angle = 90, face = "bold"),
      axis.text.y  = element_text(size = 9),
      panel.grid = element_blank(),
      plot.title = element_text(face = "bold")
      )
  }
```


### Cut-point
```{r indiv-metrics-cpval, eval=TRUE, echo=FALSE}
plotMetric(.mtc = cp.val) + ylab("Cut-point")
```


### Brier score
```{r indiv-metrics-Brier, eval=TRUE, echo=FALSE}
plotMetric(.mtc = Brier) + ylab("Brier score")
```


### AUC
* area under the ROC curve

```{r indiv-metrics-auc, eval=TRUE, echo=FALSE}
plotMetric(.mtc = auc)
```


### PR-AUC
* area under the precision-recall curve

```{r indiv-metrics-prauc, eval=TRUE, echo=FALSE}
plotMetric(.mtc = prauc) + ylab("PR-AUC")
```


### Matthews correlation coefficient
```{r indiv-metrics-mcc, eval=TRUE, echo=FALSE}
plotMetric(.mtc = mcc)
```


### Sensitivity
```{r indiv-metrics-Se, eval=TRUE, echo=FALSE}
plotMetric(.mtc = Se) + ylab("Sensitivity")
```


### Specificity
```{r indiv-metrics-Sp, eval=TRUE, echo=FALSE}
plotMetric(.mtc = Sp) + ylab("Specificity")
```


### Informedness = Youden Index
* ifd (Powers 2011) = YI

```{r indiv-metrics-ifd, eval=TRUE, echo=FALSE}
plotMetric(.mtc = ifd) + ylab("Informedness")
```


### IMN
* normalized expected mutual information (Hughes et al. 2015)
* same as NMI (Forbes 1995)

```{r indiv-metrics-IMN, eval=TRUE, echo=FALSE}
plotMetric(.mtc = IMN)
```


### MCEN
* modified confusion entropy
* recall that lower is better

```{r indiv-metrics-MCEN, eval=TRUE, echo=FALSE}
plotMetric(.mtc = MCEN)
```



## Composite plot

```{r composite-plot-functions, eval=TRUE, echo=FALSE}
# This function is taken from https://cran.r-project.org/web/packages/egg/vignettes/Ecosystem.html
# It is for combining plots, and placing a common legend.
grid_arrange_shared_legend <-
  function(...,
           ncol = length(list(...)),
           nrow = 1,
           position = c("bottom", "right")) {
    
    plots <- list(...)
    position <- match.arg(position)
    g <-
      ggplot2::ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
    legend <- g[[which(sapply(g, function(x)
      x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    lwidth <- sum(legend$width)
    gl <- lapply(plots, function(x)
      x + theme(legend.position = "none"))
    gl <- c(gl, ncol = ncol, nrow = nrow)
    
    combined <- switch(
      position,
      "bottom" = gridExtra::arrangeGrob(
        do.call(gridExtra::arrangeGrob, gl),
        legend,
        ncol = 1,
        heights = grid::unit.c(unit(1, "npc") - lheight, lheight)
      ),
      "right" = gridExtra::arrangeGrob(
        do.call(gridExtra::arrangeGrob, gl),
        legend,
        ncol = 2,
        widths = grid::unit.c(unit(1, "npc") - lwidth, lwidth)
      )
    )
    
    grid::grid.newpage()
    grid::grid.draw(combined)
    
    # return gtable invisibly
    invisible(combined)
    
  } # end function grid_arrange_shared_legend

comp.plot <- function(.df = dat2, .x, .y, .xlab, .ylab, .title) {
  # Plot variable 1 vs variable 2 for the varSelRF, VSURF, and stacked models
  # Args:
  #  .x = unquoted string for the x-axis variable
  #  .y = unquoted string for the y-axis variable
  #  .xlab = character string for the x-axis label
  #  .ylab = character string for the y-axis label
  #  .title = character string for the plot title
  # Returns:
  # a ggplot object
  #
  var1 <- enquo(.x)
  var2 <- enquo(.y)
  
  # The color scheme for the points (this will work, but decided to go with ggsci d3):
  # col.vec <- c(RColorBrewer::brewer.pal(8, "Dark2")[1:3], "deepskyblue",  RColorBrewer::brewer.pal(8, "Dark2")[5], "grey0", "grey35", "grey65", "orange", "orangered")
  
  .df %>%
    dplyr::select(!!var1, !!var2, source) %>%
    ggplot(., aes(x = !!var1, y = !!var2, colour = source, shape = source, size = source)) +
    theme_bw() +
    scale_shape_manual(values = c(16, 16, 16, 15, 17, 17, 17, 18, 18, 18)) +
    scale_size_manual(values = c(2, 2, 2, 2, 4, 4, 4, 5, 5, 5)) +
    scale_colour_d3(palette = c("category10"), alpha = 0.6) + 
    # Plot the regression first, points will go over it:
    # a robust fitting algorithm so that outliers don’t affect the fit as much:
    geom_smooth(aes(x = !!var1, y = !!var2), formula = y ~ x, method = "rlm", inherit.aes = FALSE, se = FALSE, size = 0.5, colour = "black", linetype = "dashed") +
    geom_point() +
    # change the legend position and shape:
    theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "vertical") +
    guides(colour = guide_legend(NULL, ncol = 4),
           shape = guide_legend(NULL, ncol = 4),
           size = guide_legend(NULL, ncol = 4)) +
    ylab(.ylab) +
    theme(axis.title.y = element_text(face = "bold", size = 12)) +
    theme(axis.text.y = element_text(size = rel(1.0))) +
    xlab(.xlab) +
    theme(axis.title.x = element_text(face = "bold", size = 12)) +
    theme(axis.text.x = element_text(size = rel(1.0))) +
    ggtitle(.title) +
    theme(plot.title = element_text(face = "bold"))
} # end function comp.plot
```

<!-- Prep the data for the composite plots -->
```{r composite-plot-data, eval=TRUE, echo=FALSE}
# A list of the variables we want from each stats object:
vars2 <- c("id", "source", "mcc", "Se", "Sp", "mkd", "ifd", "auc", "prauc", "MCEN", "IMN")

# Combine the stats for the various models into one object:
dat2 <-
  bind_rows(
    # The previously-reported models:
    prev.mods %>% dplyr::select(all_of(vars2)),
    # Stacked RF lasso:
    stack_lasso_metrics %>% mutate(id = "RF:Lasso", source = "RF stacked (lasso)") %>% select(all_of(vars2)),
    # Stacked RF ridge:
    stack_ridge_metrics %>% mutate(id = "RF:Ridge", source = "RF stacked (ridge)") %>% select(all_of(vars2)),
    # Stacked RF elasticnet:
    stack_en_metrics %>% mutate(id = "RF:EN", source = "RF stacked (elasticnet)") %>% select(all_of(vars2))
    ) %>%
  dplyr::mutate(source = factor(source, levels = c("LR 1st generation", "LR 2nd generation", "LR 3rd generation", "LR (weighted average)", "LR stacked (lasso)", "LR stacked (ridge)", "LR stacked (elasticnet)", "RF stacked (lasso)", "RF stacked (ridge)", "RF stacked (elasticnet)")))
```


```{r composite-plot-fig, eval=TRUE, echo=FALSE, fig.height=7.0}
# Sensitivity and specificity:
p1 <- comp.plot(.x = Se, .y = Sp, .xlab = "Se", .ylab = "Sp", .title = "A")

# Informedness and markedness:
p2 <- comp.plot(.x = ifd, .y = mkd, .xlab = "IFD", .ylab = "MKD", .title = "B")

# PR-AUC and ROC-AUC:
p3 <- comp.plot(.x = auc, .y = prauc, .xlab = "ROC-AUC", .ylab = "PR-AUC", .title = "C")

# IMN and MCEN:
p4 <- comp.plot(.x = IMN, .y = MCEN, .xlab = "IMN", .ylab = "MCEN", .title = "D")


grid_arrange_shared_legend(p1, p2, p3, p4, ncol = 2, nrow = 2)
```



# Computational environment
```{r SessionInfo, eval=TRUE, echo=FALSE, results='markup'}
R.Version()$version.string
R.Version()$system
sessionInfo()
```